### 2011-01-03 docs/slides/model.tex
Past work section complete.

	\begin{itemize}
		\item Turner(1996) and Huheey(1988):
			\begin{itemize}
				\item \textbf{Focus:} Selective pressure on prey, by learning ability of predator.
				\item Predators use simple Monte Carlo learning or mathematical approach.
			\end{itemize}
		\item Sherratt(2002):
			\begin{itemize}
				\item Co-evolving predator and prey population.
				\item Predators are deterministic, cannot learn from experience.
				\item Predators attack policy is fixed, either attack or avoid.
			\end{itemize}
	\end{itemize}
}

%-------------------------------
%More slides on Franks and Noble
%-------------------------------

\frame
{
	\frametitle{Past Work}
	\framesubtitle{Franks and Noble}

	\begin{itemize}
		\item First Model(2002):
			\begin{itemize}
				\item \textbf{Focus:} 
				\item Predators use simple Monte Carlo learning or mathematical approach.
			\end{itemize}
		\item Second Model(2004):
			\begin{itemize}
				\item Co-evolving predator and prey population.
				\item Predators are deterministic, cannot learn from experience.
				\item Predators attack policy is fixed, either attack or avoid.
			\end{itemize}
	\end{itemize}
}

%-------------------------------
%More slides on Franks and Noble
%-------------------------------

>>>>

	\begin{itemize}
		\item Turner (1996) and Huheey (1988):
			\begin{itemize}
				\item \textbf{Focus:} Selective pressure on prey, by learning ability of predator.
				\item Predators use simple Monte Carlo learning or mathematical approach.
			\end{itemize}
		\item Sherratt (2002):
			\begin{itemize}
				\item Co-evolving predator and prey population.
				\item Predators are deterministic, cannot learn from experience.
				\item Predators attack policy is fixed, either attack or avoid.
			\end{itemize}
	\end{itemize}
}

\frame
{
	\frametitle{Past Work}
	\framesubtitle{First Model by Franks and Noble}

	\begin{itemize}
		\item Multiple species are preyed upon by a single abstract predator.
		\item Appearance of the prey can evolve.
		\item Palatability is fixed.
		\item Each individual has a single gene, value representing external appearance.
		\item Phenotypes are a ring of value from 1-20 (20 and 1 are neighbors).
		\item Distance represents similarity.
		\item Predator uses simple reinforcement learning system.
		\item Three experiments carried out varying palatability of prey.
		\item Batesian mimicry was established.
	\end{itemize}
}

\frame
{
	\frametitle{Franks and Noble}
	\framesubtitle{Second Model: Working hypothesis}

	\begin{enumerate}
		\item \textsl{All of the Mullerian mimics in a given ecosystem should eventually converge into one large ring in order to gain maximum protection.}
		\item \textsl{If the Mullerian mimics do not converge into one large ring, then the presence of Batesian mimics could entice them to do so, by influencing the rings to converge.}
	\end{enumerate}
}

\frame
{
	\frametitle{Franks and Noble}
	\framesubtitle{Second Model: Prey}

	\begin{itemize}
		\item Prey population has appearance and palatability.
		\item Palatability is fixed, using different level from 0 to 1, where 0.5 is neutrally palatable.
		\item Two genes representing external appearance, using values between 1 to 200.
		\item Euclidean distance between values represents similarity.
	\end{itemize}
}

\frame
{
	\frametitle{Franks and Noble}
	\framesubtitle{Second Model: Predator}

	\begin{itemize}
		\item Monte Carlo reinforcement learning system.
		\item Predators use generation on the basis of experience.
		\item Set of probability formula was used to make decision for consumption of prey, depending on phenotype.
	\end{itemize}
}

\frame
{
	\frametitle{Franks and Noble}
	\framesubtitle{Second Model: Result}

	\begin{itemize}
		\item First Experiment:
			\begin{itemize}
				\item 20 unpalatable prey species.
				\item Hypothesis 1 of a single large ring did was not established.
				\item Multiple mimicry rings exist with different frequency.
			\end{itemize}
		\item Second Experiment:
			\begin{itemize}
				\item Some palatable and some unpalatable species.
				\item Reaches condition of Batesian mimicry. Hypothesis 2 is established.
				\item \textbf{Observation:}
					\begin{itemize}
						\item Batesian mimics provide pressure on mutants.
						\item Batesian pressure on mimicry rings push one into the range of another.
					\end{itemize}
			\end{itemize}
	\end{itemize}
}
